Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration

### 2018-07-01 chapters/introduction/introduction.tex
minor change

\section{Our Approach}
Our thesis focus on constructing a probabilistic model for camera
geo-calibration. To do that, we first develop an general architecture
for geo-calibration with different constraint functions. We then seek
to conquer constraints in subset of calibration parameters.

\begin{itemize}[noitemsep]
  \item \textbf{General Architecture for Geo-Calibration:}
  We designed a graphic model to estimate the probability over
  geo-calibration parameter space.

  \item \textbf{Constraints for Subset Parameters:}
  Divide and conquer the problems.

@@

  \item \textbf{\chapref{mcmc} - 
  Complete Camera Geo-Calibration with MCMC Method:} \newline \newline
  The complete camera geo-calibration includes the detection of camera
  location in the world, the pose and the focal length of the camera
  given the input image. By constructing a objective function that
  measures the ``matchness'' between the camera calibration and the
  observation of the image, we are able to optimize the parameters in
  the calibration space. However, this space multi-dimensional, which
  makes the naive grid search infeasible. Our insight is to do the
  optimization using Markov Chain Monte Carlo (MCMC) method. Our
  algorithm is able to avoid unnecessary sampling in the
  low-probabilistic region in the parameter space thus reduce the
  computational time dramatically. \newline

  \item \textbf{\chapref{fasthorizon} -
  Detecting Horizon and VPs using CNN:} \newline \newline
  Horizon line and vanishing points (VPs) plays important roles in many
  application such as image mensuration and facade detection. In the
  previous work, researchers tended to use build bottom-up approaches to
  solve this problem. Our work is inspired by human's perception of the
  horizon line and the vanishing point. Our method exploit the image
  global context to provide a prior distribution of the final solution,
  thus to reduce the dimensionality of the solution space. \newline

  \item \textbf{\chapref{whenwhere} -
  Learn Where with When:} \newline \newline
  One of the key to the success of machine learning approaches are the
  large quantity of annotated data. However, fully annotated imagery
  only consists of a tiny part of the image resources available online.
  The idea is to exploit other meta-info that are automatically
  recorded/captured by devices to train the ML models.  We demonstrate
  that the camera geometry can be used as weak ground truth for
  supervision problem. By learning the capture time and the geolocation
  of the images, our network is able capture the geo-temporal related
  high-level features. \newline

  \item \textbf{\chapref{crosstransf} -
  Finer Localization by Matching the Overhead Images:} \newline \newline
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. \newline

>>>>

\section{Our Approach}
We first propose primary probabilistic model to jointly estimate 
the full geo-calibration parameters. The key for the success of this
model is to construct good constraint functions that describe the
fitness between the calibration parameters and the images. We then
dismantle the full geo-calibration into several partial
geo-calibration tasks, each of which provide a constraint function to
fit in the primary model.

\begin{itemize}[noitemsep]
  \item \textbf{General Probabilistic Architecture for Geo-Calibration:}
  We design a graphic model to estimate the probability over
  full geo-calibration parameters. Our model is a general
  architecture, which can take different constraints to form
  the energy function.

  \item \textbf{Constraint Function for Camera Poses:}
  We develop a constraint function for two camera pose angles: pitch
  and roll.

  \item \textbf{Constraint Function for Camera Geographic Locations
  and Orientations:}
  We develop a constraint function for camera geographic locations and
  orientations.

@@

  \item \textbf{\chapref{mcmc} - 
  Complete Camera Geo-Calibration with MCMC Method:} \newline \newline
  The complete camera geo-calibration includes the detection of camera
  location in the world, the pose and the focal length of the camera
  given the input image. By constructing a objective function that
  measures the ``fitness'' between the camera calibration and the
  observation of the image, we are able to optimize the parameters in
  the calibration space. However, this space multi-dimensional, which
  makes the naive grid search infeasible. Our insight is to do the
  optimization using Markov Chain Monte Carlo (MCMC) method. Our
  algorithm is able to avoid unnecessary sampling in the
  low-probabilistic region in the parameter space thus reduce the
  computational time dramatically. \newline

  \item \textbf{\chapref{fasthorizon} -
  Detecting Pitch and Roll using CNN:} \newline \newline
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position in the image.
  Horizon line and vanishing points (VPs) plays important roles in many
  application such as image mensuration and facade detection. In the
  previous work, researchers tended to use build bottom-up approaches to
  solve this problem. Our work is inspired by human's perception of the
  horizon line and the vanishing point. Our method exploit the image
  global context to provide a prior distribution of the final solution,
  thus to reduce the dimensionality of the solution space. \newline

  \item \textbf{\chapref{whenwhere} -
  Estimating Geographic Location with Temporal Information:} \newline \newline
  In this work, we demonstrate that we can estimate the camera geographic
  location with the input image and its temporal information.
  One of the key to the success of machine learning approaches are the
  large quantity of annotated data. However, fully annotated imagery
  only consists of a tiny part of the image resources available online.
  The idea is to exploit other meta-info that are automatically
  recorded/captured by devices to train the ML models. We demonstrate
  that the camera geometry can be used as weak ground truth for
  supervision problem. By learning the capture time and the geolocation
  of the images, our network is able capture the geo-temporal related
  high-level features. \newline

  \item \textbf{\chapref{crosstransf} -
  Finer Localization by Matching the Overhead Images:} \newline \newline
  With the rough geographic location, we are able to refine the result
  with overhead images.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. \newline

### 2018-07-01 dissertation.tex
minor change

\abstract
{ \SingleSpacing
Camera calibration is one of the primary task in computer vision.
It plays an important role in applications like SLAM, image
mensuration and indoor layout estimation. Current models for camera
calibration are mostly deterministic, namely they output fixed
solutions. However, applications built with graphic models favor
probabilistic inputs, of which these deterministic calibration
models are not capable.
To address this problem, we propose a probabilistic model with deep
neural networks (DNNs) for camera
geo-calibration, providing more flexible inputs for applications that
are interfaced camera calibration parameters. Compared to 
traditional camera calibration, camera geo-calibration measures the
camera extrinsic in geographic coordinates.
Furthermore, our approaches also demonstrate that the geographic
information is helpful for extracting/transferring high level
features in DNN training.
The primary contributions of our thesis include building a
probabilistic model for camera geo-calibration ,and relating the
camera geographic information and image semantics through deep neural
networks. Our discoveries can provide researchers new insights for
both camera calibration and DNN training.
}
\keywords{geo-calibration, deep neural networks, computer vision}

>>>>

\abstract
{ \SingleSpacing
Camera calibration is one of the primary task in computer vision.
It plays an important role in applications like SLAM, image
mensuration and indoor layout estimation. Current models for camera
calibration are mostly deterministic, namely they output fixed
solutions. 
However, deterministic calibration models can not handle uncertainties
in our real life well. Furthermore, they are not very friendly to
graphic model algorithms with which they interface.
To address these problems, we propose a probabilistic model with deep
neural networks (DNNs) for camera geo-calibration, providing more
flexible inputs. Compared to traditional camera calibration,
camera geo-calibration measures the camera extrinsic in geographic
coordinates.  Furthermore, our approaches also demonstrate that the
geographic information is helpful for extracting/transferring high
level features in DNN training.  The primary contributions of our
thesis include building a probabilistic model for camera
geo-calibration ,and relating the camera geographic information and
image semantics through deep neural networks. Our discoveries can
provide researchers new insights for both camera calibration and DNN
training.
}
\keywords{geo-calibration, deep neural networks, computer vision}
